Type-Safe Client-Server Communication in Web Applications

### 2014-02-27 paper.tex
Fix some INTERNETS references.

\bibitem[Conductance application server (2014)]{conductance}
THE INTERNETS: http://conductance.io

@@

\bibitem[Domoszlai et al (2011)]{jsclean}
L. Domoszlai, E. Bruël, J. M. Jansen: Implementing a non-strict purely functional language in JavaScript, in Acta Universitatis Sapientiae, 2011

\bibitem[Duetto compiler (2014)]{duetto}
THE INTERNETS: http://leaningtech.com/duetto/

@@

\bibitem[The Fay language (2014)]{fay}
THE INTERNETS: http://fay-lang.org

@@

>>>>

\bibitem[Conductance application server (2014)]{conductance}
The Conductance application server, http://conductance.io

@@

\bibitem[Domoszlai et al (2011)]{jsclean}
L. Domoszlai, E. Bruël, J. M. Jansen: Implementing a non-strict purely functional language in JavaScript, Acta Universitatis Sapientiae, 2011

\bibitem[Done (2012)]{fay}
C. Done: Fay, JavaScript, etc., http://chrisdone.com/posts/fay, 2012

@@

@@

\bibitem[Pignotti (2013)]{duetto}
A. Pignotti: Duetto: a C++ compiler for the Web going beyond emscripten and node.js, http://leaningtech.com/duetto/blog/2013/10/31/Duetto-Released/, 2013
